Modeling vertical-axis cross-flow turbine wakes

### 2015-07-22 paper.tex
Add paragraph about low order modeling

Araya et al. modeled the flow through a VAT array using leaky Rankine bodies
\cite{Araya2014}.

@@

>>>>

@@

It is assumed that if the turbine power output and near-wake predictions from
the numerical model match those of the experiments, that the flow field can be
inspected in greater detail, i.e., that the experiments will have been
``interpolated''. This will allow us to see where the dominant flow structures
originate and help develop low-order wake generator models for use in turbine
array modeling. For example, Araya et al. modeled the flow through a VAT array
using leaky Rankine bodies \cite{Araya2014}. Shamsoddin and Porte-Agel modeled a 2-D CFT using large eddy simulation (LES) with an actuator line approach to impart force on the flow field \cite{Shamsoddin2014}.
